Parallelization of Fast $\ell_1$-Minimization for Face Recognition

### 2011-03-08 paper/main.tex
Added 2 of Victor's plots to the paper

The results of this benchmark can be found in Figure \ref{fig:random_data}.
The x-axis represents the size of the $A$ matrix and the y-axis represents the
average amount of time it to complete a single problem instance.  A can be seen
in Figure \ref{fig:random_data}, the GPU implementation tends to be faster than
the CPU implementation at solving a single large problem, whereas the the CPU
implementation is faster at solving a single small problem.  
\begin{figure}
\label{fig:random_data}
\begin{center}
      \includegraphics{../results/random_data/time_vs_matrix_size_constant_tol}
\end{center}
\caption{Speed vs Dimensions of A.  Outer loop tolerance = 0.1.  Inner loop tolerance = $10^{-5}$}
\end{figure}

@@

In Figure \ref{fig:alignment_stage_runtime} we report the time it takes
to align a single test image against each of the users in the gallery.
We vary the size of the gallery to show how implementation scales in the
number of gallery users.
\begin{figure}
\centering
\includegraphics[width=3.5in]{figures/alignment_stage_runtime.pdf}
\caption{Alignment Stage Time vs. Size of Training Database}
\label{fig:alignment_stage_runtime}
\end{figure}

>>>>

The results of this benchmark can be found in Figure \ref{fig:random_data}.
The x-axis represents the size of the $A$ matrix and the y-axis represents the
average amount of time it to complete a single problem instance.  A can be seen
in Figure \ref{fig:random_data}, the GPU implementation tends to be faster than
the CPU implementation at solving a single large problem, whereas the the CPU
implementation is faster at solving a single small problem.  
\begin{figure}
\begin{center}
\includegraphics[width=3.5in]{../results/random_data/time_vs_matrix_size_constant_tol}
\end{center}
\caption{Speed vs Dimensions of A.  Outer loop tolerance = 0.1.  Inner loop tolerance = $10^{-5}$}
\label{fig:random_data}
\end{figure}

\begin{figure}
\begin{center}
\includegraphics[width=3.5in]{../results/random_data/size_vs_speed_crossover_ratio_2}
\end{center}
\caption{\bf CAPTION NEEDED}
\label{fig:random_data2}
\end{figure}

@@

In Figure \ref{fig:alignment_stage_runtime} we report the time it takes
to align a single test image against each of the users in the gallery.
We vary the size of the gallery to show how implementation scales in the
number of gallery users.
%\begin{figure}
%\centering
%\include{figures/alignment_stage_runtime.tex}
%%\includegraphics[width=3.5in]{figures/alignment_stage_runtime.pdf}
%\caption{Alignment Stage Runtime vs. Size of Training Database}
%\label{fig:alignment_stage_runtime}
%\end{figure}
